\chapter{Acknowledgments}
At this point, I would like to express my gratitude to everyone who has joined me on the venture of my masters degree, may it be actively or passively. Those who offered advice and guidance when in doubt, those who motivated and inspired me to always strive for more and those who listened to me and let me spark their interest. In particular, my thank goes to my parents who have always supported me in whatever it was I set my mind on, both financially and with advice. My friends, for both sitting me down in front of my computer when I lost motivation and for taking my mind off work when sinking into it too deeply. Special thanks to Leandro Ostera and his enthusiasm for lifting my spirits, but also for all the theoretical as well as practical advice and involvement in this project.

Moreover, I want to express my gratitude to my supervisor Dr. Michael Haller for providing me with ideas, feedback and the necessary flexibility to write this thesis remotely, from Sweden. On this note, I want to also thank Oakwood Creative AB for supporting their employee's dreams and visions and the possibility for me to test my presentation software in meetings as well as Monday morning presentations. Thanks also to my colleagues here, for their constant feedback and patience with my Swedish, as well as to every last stranger I had the pleasure of telling about my research.

Finally, my admiration and appreciation go out to all developers and companies driving the course of open-source forward. Despite mostly not scientifically publishing their results, this community has given birth to some of the most exciting and most widely used technologies, libraries and frameworks on the market. Without the work of these never-resting individuals, this thesis and project would never have come into existence in their current form. To pay tribute to this vibrant community, all the work involved in this thesis was also open-sourced and published on GitHub\footnote{\href{https://github.com/irisSchaffer?tab=repositories}{\textsf{https://github.com/irisSchaffer/}}}.